i am making an edit

i am also making an edit
---
title: "Prelim Analysis"
author: "Kelsey Jensen"
date: '2023-03-20'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(lme4)
library(lmerTest)
library(emmeans)
library(car)
library(ggplot2)
```
```{r}
CFF_scenarios <- read.csv("../Data/CF_scenarios/CF22_scenarios.csv", header = TRUE)
L7_all_long <- read.csv("../Data/L7_Comparisons/L7_paired_long_scenarios.csv", header = TRUE)
L7_fields <- read.csv("L722_fields.csv", header = TRUE)
main1922_all_long <- read.csv("../Data/CF_Comparison/Main1922_all_long.csv", header = TRUE) %>% dplyr::select(-X)

```
Need to go through and replace all "0" values with NA for TCa and TCb
Is the L7 fields data also in the "all_long" version? Is there any additional info needed?

Main Farm
Years: 2019, 2022
Scenario: management perennial 
Depth: 15, 30
Plots/field: "Name"
```{r, echo = FALSE}
maindata <- main1922_all_long %>% filter(Scenario_1 != "") %>% filter(Depth != "0-30") %>% filter(TC != 0) 
maindata$unique_ID <- as.factor(maindata$x * maindata$y)
maindata$Year <- as.factor(maindata$Year)
maindata$Depth <- as.factor(maindata$Depth)
maindata$Name <- as.factor(maindata$Name)

maindata %>% ggplot(aes(x = Depth, y = TC, fill = Scenario_1)) + geom_boxplot() + facet_wrap(~Year)


lmer1 <- lmer(logit(TC/100) ~ Depth*Year*Scenario_1 + (1|Name) + (1|unique_ID), data = maindata)

plot(predict(lmer1), residuals(lmer1))
qqnorm(residuals(lmer1)); qqline(residuals(lmer1))
hist(residuals(lmer1))

summary(lmer1)
anova(lmer1)

paircomp1 <- summary((emmeans(lmer1, pairwise ~Scenario_1|Year|Depth)$contrasts))
paircomp2 <- summary((emmeans(lmer1, pairwise ~Year|Scenario_1|Depth)$contrasts))
emmeans1 <- summary(emmeans(lmer1,  ~Scenario_1+Year+Depth), type= "response")
```

Main Farm
Years: 2019, 2022
Scenario: agroforestry
Depth: 15, 30
Plots/field: "Name"
```{r, echo = FALSE}
maindata2 <- main1922_all_long %>% filter(Scenario_2 != "") %>% filter(Depth != "0-30") %>% filter(TC != 0) 
maindata2$unique_ID <- as.factor(maindata2$x * maindata2$y)
maindata2$Year <- as.factor(maindata2$Year)
maindata2$Depth <- as.factor(maindata2$Depth)
maindata2$Name <- as.factor(maindata2$Name)

maindata2 %>% ggplot(aes(x = Depth, y = TC, fill = Scenario_2)) + geom_boxplot() + facet_wrap(~Year)


lmerAg <- lmer(logit(TC/100) ~ Depth*Year*Scenario_2 + (1|Name) + (1|unique_ID), data = maindata2)

plot(predict(lmerAg), residuals(lmerAg))
qqnorm(residuals(lmerAg)); qqline(residuals(lmerAg))
hist(residuals(lmerAg))

summary(lmerAg)
anova(lmerAg)

paircompAg <- summary((emmeans(lmerAg, pairwise ~Scenario_2|Year|Depth)$contrasts))
paircompAg2 <- summary((emmeans(lmerAg, pairwise ~Year|Scenario_2|Depth)$contrasts))
emmeansAg <- summary(emmeans(lmerAg,  ~Scenario_2+Year+Depth), type= "response")
```

Main Farm
Years: 2019, 2022
Scenario: grazing
Depth: 15, 30
Plots/field: "Name"
```{r, echo = FALSE}
maindata3 <- main1922_all_long %>% filter(Scenario_3 != "") %>% filter(Depth != "0-30") %>% filter(TC != 0) 
maindata3$unique_ID <- as.factor(maindata3$x * maindata3$y)
maindata3$Year <- as.factor(maindata3$Year)
maindata3$Depth <- as.factor(maindata3$Depth)
maindata3$Name <- as.factor(maindata3$Name)

maindata3 %>% ggplot(aes(x = Depth, y = TC, fill = Scenario_3)) + geom_boxplot() + facet_wrap(~Year)


lmerGr <- lmer(logit(TC/100) ~ Depth*Year*Scenario_3 + (1|Name) + (1|unique_ID), data = maindata3)

plot(predict(lmerGr), residuals(lmerGr))
qqnorm(residuals(lmerGr)); qqline(residuals(lmerGr))
hist(residuals(lmerGr))

summary(lmerGr)
anova(lmerGr)

paircompGr <- summary((emmeans(lmerGr, pairwise ~Scenario_3|Year|Depth)$contrasts))
paircompGr2 <- summary((emmeans(lmerGr, pairwise ~Year|Scenario_3|Depth)$contrasts))
emmeansGr <- summary(emmeans(lmerGr,  ~Scenario_3+Year+Depth), type= "response")
```

Lock 7
Years: 2020, 2021, 2022
Scenario: upper v. lower
Depth: 15, 30
Plots/field: "Name"
```{r, echo = FALSE}
L7_Data1 <- L7_all_long %>% filter(Depth != 0) 
L7_Data1$unique_ID <- as.factor(L7_Data1$x * L7_Data1$y)
L7_Data1$Year <- as.factor(L7_Data1$Year)
L7_Data1$Depth <- as.factor(L7_Data1$Depth)
L7_Data1$Name <- as.factor(L7_Data1$Name)

L7_Data1 %>% ggplot(aes(x = Depth, y = TC, fill = Scenario_1)) + geom_boxplot() + facet_wrap(~Year)


lmer71 <- lmer(logit(TC/100) ~ Depth*Year*Scenario_1 + (1|Name) + (1|unique_ID), data = L7_Data1)

plot(predict(lmer71), residuals(lmer71))
qqnorm(residuals(lmer71)); qqline(residuals(lmer71))
hist(residuals(lmer71))

summary(lmer71)
anova(lmer71)

paircomp71 <- summary((emmeans(lmer71, pairwise ~Scenario_1|Year|Depth)$contrasts))
paircomp712 <- summary((emmeans(lmer71, pairwise ~Year|Scenario_1|Depth)$contrasts))
emmeans71 <- summary(emmeans(lmer71,  ~Scenario_1+Year+Depth), type= "response")
```

Lock 7
Years: 2020, 2021, 2022
Scenario: Scenario 2
Depth: 15, 30
Plots/field: "Name"
```{r}

L7_Data1 %>% ggplot(aes(x = Depth, y = TC, fill = Scenario_2)) + geom_boxplot() + facet_wrap(~Year)


lmer72 <- lmer(logit(TC/100) ~ Depth*Year*Scenario_2 + (1|Name) + (1|unique_ID), data = L7_Data1)

plot(predict(lmer72), residuals(lmer72))
qqnorm(residuals(lmer72)); qqline(residuals(lmer72))
hist(residuals(lmer72))

summary(lmer72)
anova(lmer72)

paircomp72 <- summary((emmeans(lmer72, pairwise ~Scenario_2|Year|Depth)$contrasts))
paircomp722 <- summary((emmeans(lmer72, pairwise ~Year|Scenario_2|Depth)$contrasts))
emmeans72 <- summary(emmeans(lmer72,  ~Scenario_2+Year+Depth), type= "response")
```

Lock 7
Years: 2020, 2021, 2022
Scenario: oct 2021 crop cover -> maybe just do 2021 vs 2022..? (scenario 3)
Depth: 15, 30
Plots/field: "Name"
```{r}
L7_Data1 %>% ggplot(aes(x = Depth, y = TC, fill = Scenario_3)) + geom_boxplot() + facet_wrap(~Year)


lmer73 <- lmer(logit(TC/100) ~ Depth*Year*Scenario_3 + (1|Name) + (1|unique_ID), data = L7_Data1)

plot(predict(lmer73), residuals(lmer73))
qqnorm(residuals(lmer73)); qqline(residuals(lmer73))
hist(residuals(lmer73))

summary(lmer73)
anova(lmer73)

paircomp73 <- summary((emmeans(lmer73, pairwise ~Scenario_3|Year|Depth)$contrasts))
paircomp732 <- summary((emmeans(lmer73, pairwise ~Year|Scenario_3|Depth)$contrasts))
emmeans73 <- summary(emmeans(lmer73,  ~Scenario_3+Year+Depth), type= "response")
```

Lock 7
Years: 2020, 2021, 2022
Scenario: land cover may 2022 (cover crop, millet)
Depth: 15, 30
Plots/field: "Name"
```{r}
L7_Data1 %>% ggplot(aes(x = Depth, y = TC, fill = Scenario_4)) + geom_boxplot() + facet_wrap(~Year)


lmer74 <- lmer(logit(TC/100) ~ Depth*Year*Scenario_4 + (1|Name) + (1|unique_ID), data = L7_Data1)

plot(predict(lmer74), residuals(lmer74))
qqnorm(residuals(lmer74)); qqline(residuals(lmer74))
hist(residuals(lmer74))

summary(lmer74)
anova(lmer74)

paircomp74 <- summary((emmeans(lmer74, pairwise ~Scenario_4|Year|Depth)$contrasts))
paircomp742 <- summary((emmeans(lmer74, pairwise ~Year|Scenario_4|Depth)$contrasts))
emmeans74 <- summary(emmeans(lmer74,  ~Scenario_4+Year+Depth), type= "response")
```

